---
title: "Assignment_1_Wage_PhakphumJ"
author: "Phakphum Jatupitpornchan"
format: html
editor: visual
---

```{r}
#| warning: false
#| echo: false

rm(list=ls())

setwd("D:/Onedrive-CEU/OneDrive - Central European University/CEU/Prediction with Machine Learning/Assignment/DA3-phdma/Assignment 1")

library(readr)
library(dplyr)

# Importing the data

DataOriginal <- read_csv("morg-2014-emp.csv")

# Filter - only select 'Miscellaneous agricultural workers, including animal breeders' - 6050

MiscWorkerData = DataOriginal %>%
  filter(occ2012 == 6050)
```

# Assignment 1

The task is to build a model to predict hourly earnings. I select 'Miscellaneous agricultural workers, including animal breeders' (*occ2012* = 6050) to be my population of interest.\

Firstly, I describe the variables that will be used in constructing the models. Then, the details of each model are presented along with the performance. Finally, I discuss the obtained results.

## Data Dictionary

### Original Variables

This section describes the meaning of each variable that will be used in this modelling exercise.

-   stfips: State codes

-   weight: Final Weight

-   earnwke: Earnings per week

-   uhours: Working hours per week

-   grade92: Highest grade attended

-   race: Race (1 = White, 2 = Black, 3 = American Indian (AI), 4 = Asian, 5 = Hawaiian/Pacific Islander, 6 = White-Black, 7 = White-AI, 8 = White-Asian)

    ```{r}
    #| echo = FALSE

    ## I run this code to see what races are there in this dataset
    MiscWorkerData %>% count(race)
    ```

I will group some races above together later.

-   age: Age

-   sex: Sex (1 = male, 2 = female)

-   marital: Marital Status (1 = Married civilian spouse present, 2 = Married Armed Foruces spouse present, 3 = Married spouse absent or separated, 4 = Widowed or divorced(Through 88), 5 = Widowed (After 88), 6 = Separated , 7 = Never Married)

    ```{r}
    #| echo: false
    MiscWorkerData %>% count(marital)
    ```

I will group some marital statuses above together later.

-   ownchild: Number of own children **less than** **18** in primary family

-   prcitshp: Citizenship status

    ```{r}
    #| echo: false
    MiscWorkerData %>% count(prcitshp)
    ```

I will group some citizenship statuses above together later.

-   ind02: 3-digit NAICS-based industry code

-   class: Class of worker

    ```{r}
    #| echo: false
    MiscWorkerData %>% count(class)
    ```

I will group some classes above together later.\
 

I discard *chldpres* since it is highly correlated with *ownchild*.

I discard *unionmme* and *unioncov* since 99% of the sample have these two variables = 0.

I discard *lfsr94* since every observations in my sample is employed in the previous week.

*ethnic* is also discarded since it mainly describes the ethnicity of Hispanic workers ,which I think might not be very useful.

### Generated / Transformed Variables

```{r}
#| echo: false
# Defining the target variable
MiscWorkerData = MiscWorkerData %>% mutate(earnhr = earnwke/uhours)

# grouping race. (1. white 2. black 3. non-white/black)
# Create is_white and is_black variables - use non-white/black as baseline

MiscWorkerData = MiscWorkerData %>% mutate(is_white = case_when(race == 1 ~ 1, race != 1 ~ 0), is_black = case_when(race == 2 ~ 1, race != 2 ~ 0))

# grouping marital statuses. (1. Married with spouse present 2. Married with spouse absent or seperated 3. Widowed or divorced 4. Never Married) - leave the first category out to be baseline

MiscWorkerData = MiscWorkerData %>% mutate(marr_abs = case_when(marital == 3 ~ 1, marital != 3 ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(wid_div = case_when(marital == 4 | marital == 5 | marital == 6 ~ 1, marital != 4 | marital != 5 | marital != 6 ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(nevmarr = case_when(marital == 7 ~ 1, marital != 7 ~ 0))

# Recode gender 1 = male, 0 = female. Use female as baseline
MiscWorkerData = MiscWorkerData %>% mutate(male = case_when(sex == 1 ~ 1, sex != 1 ~ 0))

# grouping citizen ship status. (1. Foreign Born, Not a US Citizen 2. Foreign Born, US Cit By Naturalization 3. Native) - use Native as baseline
MiscWorkerData = MiscWorkerData %>% mutate(noncitiz = case_when(prcitshp == 1 ~ 1, prcitshp != 1 ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(natura = case_when(prcitshp == 2 ~ 1, prcitshp != 2 ~ 0))

# grouping classes of worker (1. Private, For Profit, 2. Others) use Others as the baseline
MiscWorkerData = MiscWorkerData %>% mutate(forprofit = case_when(class == 4 ~ 1, class != 4 ~ 0))

```

The target variable: (earnings per hour)

## Model Building

## Performance

## Discussion
