---
title: "Assignment1_Wage_PhakphumJ"
author: "Phakphum Jatupitpornchan"
format: html
editor: visual
---

```{r}
#| warning: false
#| echo: false

rm(list=ls())

setwd("D:/Onedrive-CEU/OneDrive - Central European University/CEU/Prediction with Machine Learning/Assignment/DA3-phdma/Assignment 1")

library(readr)
library(dplyr)

# Importing the data

DataOriginal <- read_csv("morg-2014-emp.csv")

# Filter - only select 'Miscellaneous agricultural workers, including animal breeders' - 6050

MiscWorkerData = DataOriginal %>%
  filter(occ2012 == 6050)
```

# Assignment 1

## Data Dictionary

### Original Variables

This section describes the meaning of each variable that will be used in this modelling exercise.

-   stfips: State codes

-   weight: Final Weight

-   earnwke: Earnings per week

-   uhours: Working hours per week

-   grade92: Highest grade attended

-   race: Race (1 = White, 2 = Black, 3 = American Indian (AI), 4 = Asian, 5 = Hawaiian/Pacific Islander, 6 = White-Black, 7 = White-AI, 8 = White-Asian)

    ```{r}
    #| echo = FALSE

    ## I run this code to see what races are there in this dataset
    MiscWorkerData %>% count(race)
    ```

I will group some races above together later

-   age: Age

-   sex: Sex (1 = male, 2 = female)

-   marital: Marital Status (1 = Married civilian spouse present, 2 = Married Armed Foruces spouse present, 3 = Married spouse absent or separated, 4 = Widowed or divorced(Through 88), 5 = Widowed (After 88), 6 = Separated , 7 = Never Married)

    ```{r}
    #| echo: false
    MiscWorkerData %>% count(marital)
    ```

I will group some marital statuses above together later

-   ownchild: Number of own children **less than** **18** in primary family
-   prcitshp: Citizenship status

```{r}
#| echo: false
MiscWorkerData %>% count(prcitshp)
```

I will group some citizenship statuses above together later

-   ind02: 3-digit NAICS-based industry code

-   class: Class of worker

```{r}
#| echo: false
MiscWorkerData %>% count(class)
```

I will group some classes above together later

-   unionmme: Is a member of a labor union or an employee association similar to a union

### Transformed Variables
