---
title: "Assignment_1_Wage_PhakphumJ"
author: "Phakphum Jatupitpornchan"
format: html
editor: visual
---

```{r}
#| warning: false
#| echo: false

rm(list=ls())

setwd("D:/Onedrive-CEU/OneDrive - Central European University/CEU/Prediction with Machine Learning/Assignment/DA3-phdma/Assignment 1")

library(readr)
library(dplyr)
library(ggplot2)
library(weights)
library(caret)


# Importing the data

DataOriginal <- read_csv("morg-2014-emp.csv")

# Filter - only select 'Miscellaneous agricultural workers, including animal breeders' - 6050

MiscWorkerData = DataOriginal %>%
  filter(occ2012 == 6050)
```

# Assignment 1

The task is to build a model to predict hourly earnings. I select 'Miscellaneous agricultural workers, including animal breeders' (*occ2012* = 6050) to be my population of interest.\

Firstly, I describe the variables that will be used in constructing the models. Then, the details of each model are presented along with the performance. Finally, I discuss the obtained results.

## Data Dictionary

### Original Variables

This section describes the meaning of each variable that will be used in this modelling exercise.

-   stfips: State codes

-   weight: Final Weight

-   earnwke: Earnings per week

-   uhours: Working hours per week

-   grade92: Highest grade attended; **It is not numerical variable**. (e.g. 31 = Less than 1st grade, 32 = 1st - 4th grade)

```{r}
#| echo: false
MiscWorkerData %>% count(grade92)
```

I will group some education levels above together later.

-   race: Race (1 = White, 2 = Black, 3 = American Indian (AI), 4 = Asian, 5 = Hawaiian/Pacific Islander, 6 = White-Black, 7 = White-AI, 8 = White-Asian)

    ```{r}
    #| echo = FALSE

    ## I run this code to see what races are there in this dataset
    MiscWorkerData %>% count(race)
    ```

I will group some races above together later.

-   age: Age

-   sex: Sex (1 = male, 2 = female)

-   marital: Marital Status (1 = Married civilian spouse present, 2 = Married Armed Foruces spouse present, 3 = Married spouse absent or separated, 4 = Widowed or divorced(Through 88), 5 = Widowed (After 88), 6 = Separated , 7 = Never Married)

    ```{r}
    #| echo: false
    MiscWorkerData %>% count(marital)
    ```

I will group some marital statuses above together later.

-   ownchild: Number of own children **less than** **18** in primary family

-   prcitshp: Citizenship status

    ```{r}
    #| echo: false
    MiscWorkerData %>% count(prcitshp)
    ```

I will group some citizenship statuses above together later.

-   ind02: 3-digit NAICS-based industry code

-   class: Class of worker

    ```{r}
    #| echo: false
    MiscWorkerData %>% count(class)
    ```

I will group some classes above together later.\
 

I discard *chldpres* since it is highly correlated with *ownchild*.

I discard *unionmme* and *unioncov* since 99% of the sample have these two variables = 0.

I discard *lfsr94* since every observations in my sample are employed in the previous week.

*ethnic* is also discarded since it mainly describes the ethnicity of Hispanic workers ,which I think might not be very useful. It also contains 8 categories. If included, we would lose quite some degree of freedom.

### Generated Variables

```{r}
#| echo: false
# Defining the target variable
MiscWorkerData = MiscWorkerData %>% mutate(earnhr = earnwke/uhours)

# grouping race. (1. white 2. black 3. non-white/black)
# Create is_white and is_black variables - use non-white/black as baseline

MiscWorkerData = MiscWorkerData %>% mutate(is_white = case_when(race == 1 ~ 1, race != 1 ~ 0), is_black = case_when(race == 2 ~ 1, race != 2 ~ 0))

# grouping marital statuses. (1. Married with spouse present 2. Married with spouse absent or seperated 3. Widowed or divorced 4. Never Married) - leave the first category out to be baseline

MiscWorkerData = MiscWorkerData %>% mutate(marr_abs = case_when(marital == 3 ~ 1, marital != 3 ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(wid_div = case_when(marital == 4 | marital == 5 | marital == 6 ~ 1, marital != 4 | marital != 5 | marital != 6 ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(nevmarr = case_when(marital == 7 ~ 1, marital != 7 ~ 0))

# Recode gender 1 = male, 0 = female. Use female as baseline
MiscWorkerData = MiscWorkerData %>% mutate(male = case_when(sex == 1 ~ 1, sex != 1 ~ 0))

# grouping citizen ship status. (1. Foreign Born, Not a US Citizen 2. Foreign Born, US Cit By Naturalization 3. Native) - use Native as baseline
MiscWorkerData = MiscWorkerData %>% mutate(noncitiz = case_when(prcitshp == 'Foreign Born, Not a US Citizen' ~ 1, prcitshp != 'Foreign Born, Not a US Citizen' ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(natura = case_when(prcitshp == 'Foreign Born, US Cit By Naturalization' ~ 1, prcitshp != 'Foreign Born, US Cit By Naturalization' ~ 0))

# grouping classes of worker (1. Private, For Profit, 2. Others) use Others as the baseline
MiscWorkerData = MiscWorkerData %>% mutate(forprofit = case_when(class == 'Private, For Profit' ~ 1, class != 'Private, For Profit' ~ 0))

# grouping education levels (1. 6th grade or less 2. 7th - 12th grade but NO Diploma, 3. High school graduate, diploma or GED 4. Some college but no degree 5. Associate degree 6. Bachelor's degree or more) - use 6th grade or less as baseline
MiscWorkerData = MiscWorkerData %>% mutate(than7nodip = case_when(between(grade92, 34, 38) ~ 1, !between(grade92, 34, 38) ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(HS_GED = case_when(grade92 == 39 ~ 1, grade92 != 39 ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(Col_ND = case_when(grade92 == 40 ~ 1, grade92 != 40 ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(asscd = case_when(between(grade92, 41, 42) ~ 1, !between(grade92, 41, 42) ~ 0))

MiscWorkerData = MiscWorkerData %>% mutate(Bach_more = case_when(grade92 >= 43 ~ 1, !grade92 >= 43 ~ 0))
```

```{r}
#| warning: false
#| echo: false


## Added data about minimum wages
minwage = read_csv("Minwage_2014.csv")

# Left join into the main data
MiscWorkerData <- MiscWorkerData %>% left_join(minwage, by = c("stfips" = "State"))
```

The generated variables are:

-   earnhr: Earning per hour **(This is the target variable)**

#### Race

-   is_white: 1 if race is white; 0 otherwise

-   is_black: 1 if race is black; 0 otherwise

#### Marital Status

-   marr_abs: 1 if married with spouse absent or separated; 0 otherwise

-   wid_div: 1 if widowed or divorced; 0 otherwise

-   nevmarr: 1 if never married; 0 otherwise

#### Gender

-   male: 1 if male; 0 otherwise

#### Citizenship Status

-   noncitiz: 1 if not a US citizen; 0 otherwise

-   natura: 1 if Foreign Born, US citizen by Naturalization; 0 otherwise

#### Class

-   forprofit: 1 if working in private in for-profit private organization; 0 otherwise

#### Education Level

-   than7nodip: 1 if 7th - 12th grade but NO Diploma; 0 otherwise

-   HS_GED: 1 if High school graduate, diploma or GED; 0 otherwise

-   Col_ND: 1 if Some college but no degree;; 0 otherwise

-   asscd: 1 if Associate degree; 0 otherwise

-   Bach_more: 1 if Bachelor's degree or more; 0 otherwise

#### Minimum Wage

The sample comes from 50 states. While each state may have different social and economic environment, we would lose significant degree of freedom if we use *stfips*. To compromise, I opt to use data on minimum wages of each state instead. I use published data on the government website and asked ChatGPT to clean it [^1].

[^1]: The data is from :https://www.dol.gov/agencies/whd/state/minimum-wage/history; the recorded process with ChatGPT can be accessed by: https://chat.openai.com/share/dd30493f-c0f8-4b6e-ba9e-ea05e228c719

-   Minwage: the minimum wages in each states in 2014.

## Model Building

I use correlations between the target variable and features to help ordering which variables enter into the models.

```{r}
#| echo: false
## Selecting drop irrelevant variables
WorkingData = MiscWorkerData %>% select(-c(...1, hhid, intmonth, earnwke, race, ethnic, sex, marital, chldpres, prcitshp, state, occ2012, class, unionmme, unioncov, lfsr94, grade92, stfips))
```


```{r}
#| echo: false
#| warning: false

# Calculating correlations matrix. (Only numeric variables)
# weighted correlations
data_mat = as.matrix(WorkingData[,-c(5)])

correlations = wtd.cors(x = data_mat[,-c(1)], y = data_mat[,5], weight = data_mat[,1])

# Put it into table
target_correlations <- data.frame(correlations)
```

```{r}
#| echo: false
# Print the correlations
print(target_correlations)
```


**The specification of each model is:**

**Model 1:** *earnhr* = *f(age, marr_abs, wid_div, nevmarr, noncitiz, natura, than7nodip, HS_GED, Col_ND, asscd, Bach_more)* \
&nbsp;\
Essentially, age, marital status, citizenship status, and education level are used. These features have the highest correlation with *earnhr*\


**Model 2:** **Model 1** + *(uhours, is_white, is_black, forprofit)*\
&nbsp;\ 
&nbsp;\
which means adding working hours, race, and class of worker to **Model 1** These variables have the next highest values of correlations.\

**Model 3:** **Model 2** + *(male, ownchild)*\
&nbsp;\
meaning that I add gender and number of children to the model.\

**Model 4:** **Model 3** + *(Minwage, ind02)*\
&nbsp; \
accounts for the variation in minumum wages across state. I added ind02 at the last step because it significantly increases the number of parameters to be estimated \

```{r}
#| echo: false
#| warning: false
## Doing One-Hot Encoding to ind02 to get dummies
# Assuming your data is stored in a variable called 'data' and the nominal variable is 'nominal_variable'
dummy_data <- dummyVars(~ ind02, data = WorkingData)

# Apply the transformation to your data
data_encoded <- predict(dummy_data, newdata = WorkingData)

WorkingData = cbind(WorkingData, data_encoded)

```

```{r}
#| echo: false
#| warning: false
# Doing 5-folds CV
set.seed(2023)
# Getting index for splitting data
folds <- createFolds(WorkingData$earnhr, k = 5, list = TRUE, returnTrain = FALSE)

```

```{r}
#| echo: false
#| warning: false
## Estimating Models and obtains results (5-folds CV)
# Model 1
results <- list()
for (i in 1:5) {
  train_data <- WorkingData[-folds[[i]], ]
  test_data <- WorkingData[folds[[i]], ]
  
  # Train your OLS model
  model_1 <- lm(earnhr ~ age + marr_abs + wid_div + nevmarr + noncitiz + natura + than7nodip + HS_GED + Col_ND + asscd + Bach_more, weights = weight, data = train_data) 
  # Assuming 'target_variable' is the variable you're trying to predict, 
  # and you want to use all other variables as predictors
  
  # Test your model
  predictions <- predict(model_1, newdata = test_data)
  
  # Calculate performance metric MSE
  mse <- mean((test_data$earnhr - predictions)^2)
  
  # Store the results
  results[[i]] <- mse
}
  
  # Get average RMSE
RMSE_CV_Model1 = sqrt(mean(unlist(results)))
  

# Model 2
results <- list()
for (i in 1:5) {
  train_data <- WorkingData[-folds[[i]], ]
  test_data <- WorkingData[folds[[i]], ]
  
  # Train your OLS model
  model_2 <- update(model_1, .~. + uhours, is_white, is_black, forprofit) 
  # Assuming 'target_variable' is the variable you're trying to predict, 
  # and you want to use all other variables as predictors
  
  # Test your model
  predictions <- predict(model_2, newdata = test_data)
  
  # Calculate performance metric MSE
  mse <- mean((test_data$earnhr - predictions)^2)
  
  # Store the results
  results[[i]] <- mse
}
  
  # Get average RMSE
RMSE_CV_Model2 = sqrt(mean(unlist(results)))


# Model 3

results <- list()
for (i in 1:5) {
  train_data <- WorkingData[-folds[[i]], ]
  test_data <- WorkingData[folds[[i]], ]
  
  # Train your OLS model
  model_3 <- update(model_2, .~. + male, ownchild)
  # Assuming 'target_variable' is the variable you're trying to predict, 
  # and you want to use all other variables as predictors
  
  # Test your model
  predictions <- predict(model_3, newdata = test_data)
  
  # Calculate performance metric MSE
  mse <- mean((test_data$earnhr - predictions)^2)
  
  # Store the results
  results[[i]] <- mse
}
  
  # Get average RMSE
RMSE_CV_Model3 = sqrt(mean(unlist(results)))


#Model 4
results <- list()
for (i in 1:5) {
  train_data <- WorkingData[-folds[[i]], ]
  test_data <- WorkingData[folds[[i]], ]
  
  # Train your OLS model
  model_4 <- lm(earnhr ~ . -weight, weights = weight, data = train_data[, -c(5)])
  # Assuming 'target_variable' is the variable you're trying to predict, 
  # and you want to use all other variables as predictors
  
  # Test your model
  predictions <- predict(model_4, newdata = test_data)
  
  # Calculate performance metric MSE
  mse <- mean((test_data$earnhr - predictions)^2)
  
  # Store the results
  results[[i]] <- mse
}
  
  # Get average RMSE
RMSE_CV_Model4 = sqrt(mean(unlist(results)))

```
```{r}
## Estimating using the whole sample. Get BIC and RMSE

## Model 1
model_1 <- lm(earnhr ~ age + marr_abs + wid_div + nevmarr + noncitiz + natura + than7nodip + HS_GED + Col_ND + asscd + Bach_more, weights = weight, data = WorkingData) 

# Calculate RMSE in full sample

predictions <- predict(model_1, newdata = WorkingData)
  
# Calculate performance metric RMSE
rmse_full_Model1 <- sqrt(mean((WorkingData$earnhr - predictions)^2))


## Model 2
model_2 <- update(model_1, .~. + uhours, is_white, is_black, forprofit) 

# Calculate RMSE in full sample

predictions <- predict(model_2, newdata = WorkingData)
  
# Calculate performance metric RMSE
rmse_full_Model2 <- sqrt(mean((WorkingData$earnhr - predictions)^2))

## Model 3
model_3 <- update(model_2, .~. + male, ownchild)

# Calculate RMSE in full sample

predictions <- predict(model_3, newdata = WorkingData)
  
# Calculate performance metric RMSE
rmse_full_Model3 <- sqrt(mean((WorkingData$earnhr - predictions)^2))

## Model 4
model_4 <- lm(earnhr ~ . -weight, weights = weight, data = WorkingData[, -c(5)])

# Calculate RMSE in full sample

predictions <- predict(model_4, newdata = WorkingData)
  
# Calculate performance metric RMSE
rmse_full_Model4 <- sqrt(mean((WorkingData$earnhr - predictions)^2))


```


## Performance

## Discussion
